Hippocampal replay of experience at real-world speeds

### 2020-12-16 Article.tex

@@

% Figure 3-Supplemental 2
\figsupp[Comparison of percentage of SWRs classified on real vs. position shuffled data]{Comparison of percentage of SWRs classified (that is, a SWR containing at least one of the five classifications) on real vs. position shuffled data for two epochs from different animals. Red line represents the percent of SWR events classified in that epoch for real data. The histogram represents the distribution after 50 shuffles of the position data. Position data was shuffled by resampling with replacement from the set of all observed positions in that epoch, destroying position information but preserving spiking timing and position occupancy.}{\includegraphics[width=0.8\linewidth]{figures/Figure3-supplemental2/Figure3_v2-supplemental2}}\label{figsupp:fig3sup2}
\end{figure}

@@

We find that spatially coherent events indeed have smaller HPD regions than events with fragmented dynamics. \FIG{4}A and \FIG{4}D show two example SWRs that are classified as having stationary and continuous dynamics, respectively. The most probable positions (as estimated by the model) at each time step in these SWRs is concentrated in a small portion of the track and correspondingly, the HPD region is small throughout the SWRs. In contrast, \FIG{4}C shows a SWR where the dynamics are fragmented and correspondingly, the most probable positions are more spatially diffuse and the HPD region is much larger. The HPD region size also provides insights into the moment-by-moment structure of each event, which can change over the time course of a SWR. An example of this change is shown in \FIG{4}B, where the HPD region is small for most of the SWR until the end, at which point the uncertainty of position becomes much higher, reflecting a transition from a spatially coherent to a spatially incoherent representation. Overall, when we examine the average HPD region size for each SWR, grouped by dynamic, we find a clear bimodal split between spatially coherent dynamics and spatially incoherent dynamics (\FIG{4}E). For the spatially coherent dynamics, the average HPD region for each SWR was much smaller than the spatially incoherent dynamics (median 24 cm, spatially coherent vs. median 238 cm, spatially incoherent, p=2.2e-16, one-sided Mann-Whitney-U). Additionally, the HPD region for the unclassified SWRs was similarly large. We note here that while the size of the HPD region will be influenced by the dynamic estimated from the data, it remains possible for continuous or stationary dynamics to correspond to a large HPD region (see outliers in \FIG{4}E), indicating less spatial certainty for those specific events. In general, if the data does not exhibit strong place specific firing, the HPD region will be large, regardless of dynamic classification. To show this, we resampled position with replacement for two recording sessions, shuffling the relationship between spiking and spatial information and then fitting the encoding model. The shuffled decodes have much larger HPD regions than the real data (epoch \#1: 55 cm vs. 229 cm, p=0.02, real vs. shuffled; epoch \#2: 72 cm vs. 231 cm, p=0.02, real vs. shuffled; one-sided Mann-Whitney-U, \FIGSUPP[4]{fig4sup1}.

@@

>>>>

% Figure 2-video1
\videosupp{Example of a SWR with continuous content. Magenta dot represents the animal's position. Green dot represents the most likely decoded position projected from 1D back to the linearized 2D position. Green line represents the decoded positions in the last 10 ms. Grey lines represent the position of the animal over the course of the epoch.}\label{videosupp:fig2supv1}

@@

% Figure 3-Supplemental 2
\figsupp[Comparison of percentage of SWRs classified on real vs. position shuffled data]{Comparison of percentage of SWRs classified (that is, a SWR containing at least one of the five classifications) on real vs. position shuffled data for two epochs from different animals. Red line represents the percent of SWR events classified in that epoch for real data. The histogram represents the distribution after 50 shuffles of the position data. Position data was shuffled by resampling with replacement from the set of all observed positions in that epoch, destroying position information but preserving spiking timing and position occupancy.}{\includegraphics[width=0.8\linewidth]{figures/Figure3-supplemental2/Figure3_v2-supplemental2}}\label{figsupp:fig3sup2}

% Figure 3-video1
\videosupp{Example of a SWR with that is not purely continuous. Conventions the same as Figure 2-video1}\label{videosupp:fig3supv1}

@@

We find that spatially coherent events indeed have smaller HPD regions than events with fragmented dynamics. \FIG{4}A and \FIG{4}D show two example SWRs that are classified as having stationary and continuous dynamics, respectively. The most probable positions (as estimated by the model) at each time step in these SWRs is concentrated in a small portion of the track and correspondingly, the HPD region is small throughout the SWRs. In contrast, \FIG{4}C shows a SWR where the dynamics are fragmented and correspondingly, the most probable positions are more spatially diffuse and the HPD region is much larger. The HPD region size also provides insights into the moment-by-moment structure of each event, which can change over the time course of a SWR. An example of this change is shown in \FIG{4}B, where the HPD region is small for most of the SWR until the end, at which point the uncertainty of position becomes much higher, reflecting a transition from a spatially coherent to a spatially incoherent representation. Overall, when we examine the average HPD region size for each SWR, grouped by dynamic, we find a clear bimodal split between spatially coherent dynamics and spatially incoherent dynamics (\FIG{4}E). For the spatially coherent dynamics, the average HPD region for each SWR was much smaller than the spatially incoherent dynamics (median 24 cm, spatially coherent vs. median 238 cm, spatially incoherent, p=2.2e-16, one-sided Mann-Whitney-U). Additionally, the HPD region for the unclassified SWRs was similarly large. We note here that while the size of the HPD region will be influenced by the dynamic estimated from the data, it remains possible for continuous or stationary dynamics to correspond to a large HPD region (see outliers in \FIG{4}E), indicating less spatial certainty for those specific events. In general, if the data does not exhibit strong place specific firing, the HPD region will be large, regardless of dynamic classification. To show this, we resampled position with replacement for two recording sessions, shuffling the relationship between spiking and spatial information and then fitting the encoding model. The shuffled decodes have much larger HPD regions than the real data (epoch \#1: 55 cm vs. 229 cm, p=0.02, real vs. shuffled; epoch \#2: 72 cm vs. 231 cm, p=0.02, real vs. shuffled; one-sided Mann-Whitney-U, \FIGSUPP[4]{fig4sup1}).

@@

% Figure 5-video1
\videosupp{Example of a stationary-continuous-mixture. Conventions the same as Figure 2-video1}\label{videosupp:fig5supv1}
